Secontrails plots

### 2022-01-18 R/Secontrails plots.Rmd

# Data
```{r}
# save(secondtrails, file = "../data/secondtrails.Rdata")
data("HarvestablePolygons")
data("MainTrails")
```

@@

# Plots
```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "Paracou P6 zones exploitables") +

>>>>

# Data
```{r}
# save(secondtrails, file = "../data/secondtrails.Rdata")
data("HarvestablePolygons")
data(DTMParacou)
data(CreekDistances)
data("MainTrails")
```

# Def UP
```{r}
HarvestableAreaOutputs27 <- harvestableareadefinition(
  topography = DTMParacou,
  creekdistances = CreekDistances,
  advancedloggingparameters = loggingparameters(MaxAreaSlope = 27)
)
HarvesPolygons22 <-  HarvestableAreaOutputs$HarvestablePolygons
HarvesPolygons27 <-  HarvestableAreaOutputs27$HarvestablePolygons

HarvestableAreaOutputs27$HarvestableArea # 6.0683
HarvestableAreaOutputs$HarvestableArea # 6.0683

PlotSlope <-  HarvestableAreaOutputs$PlotSlope
```

@@

# Plots
```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvesPolygons27,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "Paracou P6 zones exploitables 22 et 27% de pente")+
  geom_sf(data = HarvesPolygons22,
          aes(alpha = Harvestable),
          fill = "pink")
